---
title: "W_UP_01"
author: "Michael Maida"
date: "Fall 2020"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called push-ups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

The goal of this data analysis was to discover how the amount of push-ups a football player could do in two minutes would correlate to their position on the field. We divided the roles of football players on the field into two different categories: players whose position forced them to run around were "skill" players, while positions that required more body mass were "line" players. The hypothesis of this experiment is that there was a clear correlation between the average number of push-ups line and skill player could do in a 2-minute sitting.  
  
$H_A$: The average number of pushups done by line players is statistically different than that of skill players.  

In contrast, the null hypothesis predicts little to no difference between the averages.  
  
$H_0$: There is no difference between the average number of push-ups of line vs skill players.  

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

To determine the accuracy of the hypothesis, two different forms of variable analysis were used. First, a box plot was created to visually convey the outliers, interquartile ranges, medians, and quartiles. Second, a data frame was utilized to ascertain specific numerical differences between two positions' minima, maxima, standard deviations, etc.

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Plot boxplots

```{r}
boxplot(pushups~position, data=mydata)
```

The skill players average more push-ups than the line players.
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position, data=mydata)
```
While the skill players deviated more than the skill players in the amount of push-ups they could do, they still contained the far greater mean and median of push-ups.
## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position, data=mydata)
```
The P-value is 0.000009421. Because this value is so small, we reject the null hypothesis. Skill players can do more pushups on average in two minutes than can line players.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
The original question was whether or not there is a difference between the average number of push-ups that skill and line players can do. To find the differences, we plotted a box plot. To find the averages, we calculated the numerical summaries. The skill players can do more pushups in 2 minutes than the line players.
